Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-03-18 icmssp-paper/parts/02_02_cryptoimg.tex
Finished first pass of revisions

\subsection{CryptoImg}
A paper published in 2009 by Ziad, et al. implements privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. The \textit{CryptoImg} library assumed a client-server model wherein a client requests image processing operations from a server. A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents. The resulting image is sent back to the client, which decrypts the image to recover the desired output.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
    \label{fig:clientserver}
\end{figure}

The \textit{CryptoImg} library implemented the following image processing operations: image negation, brightness adjustment, spatial filters (for noise reduction, edge detection and sharpening), morphological operations, and histogram equalization.

@@

Ziad, et al. also showed experimental results establishing the relatively slow performance of image operations under a homomorphic cryptosystem. For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.

@@

% Convert to single table
\subsection{Image Intensity Transformations}
We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which is applied to every pixel $r$ in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control. An image negation transformation is defined as
\begin{equation}
    T\left(r\right) = L-1-r,
\end{equation}
which results in an image similar to a photographic negative~\cite{gonzalez_digital_2008}.
A brightness control transformation with parameter $v$ is defined as
\begin{equation}
    T\left(r,v\right) = r+v.
\end{equation}
The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.

In this study we extend the range of intensity transformations to non-linear transformations. Two common non-linear image transformations are the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}.

The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}. This has the general formula
\begin{equation}
    T\left(r\right) = c \log\left(1 + r\right)
\end{equation}
where $c$ is a constant.
The power-law transformation is a family of transformations that have the form
\begin{equation}
    T\left(r\right) = c r^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$.
A power-law transformation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
% This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.

To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. An applicable approximation for the logarithm may be found in \cite{pcsc-paper}. 
% In our software library implementation, we investigate methods required to approximate the logarithm and power functions. 
Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.

>>>>

\subsection{Intensity Transformations in CryptoImg}
A paper published in 2009 by Ziad, et al. implements privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. The \textit{CryptoImg} library assumed a client-server model wherein a client requests image processing operations from a server. A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents. The resulting image is sent back to the client, which decrypts the image to recover the desired output.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
    \label{fig:clientserver}
\end{figure}

An intensity transformation on a digital image $R$ can be defined as a function $T$ which is applied to every pixel $r$ in $R$. Table \ref{tab:imageoperation_summary} shows common image intensity transformations~\cite{gonzalez_digital_2008}.

% The \textit{CryptoImg} library implemented the following image processing operations: image negation, brightness adjustment, spatial filters (for noise reduction, edge detection and sharpening), morphological operations, and histogram equalization. 
The \textit{CryptoImg} library implemented two types of intensity transformations: image negation and brightness control, which are both linear transformations. In this study,we consider two common non-linear transformations. the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}, seen in Table \ref{tab:imageoperation_summary}.

@@

% Ziad, et al. also showed experimental results establishing the relatively slow performance of image operations under a homomorphic cryptosystem. For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.

@@

% Convert to single table
\begin{table}[ht]
	\caption{Summary of intensity transformations}
	\label{tab:imageoperation_summary}
    \begin{tabular}{
        p{\dimexpr 0.65\linewidth-2\tabcolsep}
        p{\dimexpr 0.35\linewidth-2\tabcolsep}}
		\toprule
		Operation & Transformation\\
        \midrule
            Image negation &
            $T\left(r\right) = L-1-r$
            \\
            Brightness adjustment transformation with parameter $v$ &
            $T\left(r\right) = r+v$
            \\
            Logarithm transformation with parameter $c$ &
            $T\left(r\right) = c \log\left(1 + r\right)$\\
            Power-law transformation with parameters $c$ and $\gamma$, where $c>0$ and $\gamma > 0$&
            $T\left(r\right) = c r^{\gamma}$\\
	    \bottomrule
    \end{tabular}
\end{table}
% We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values. A power-law transformation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}~\cite{gonzalez_digital_2008}. Both of these transformation can be used in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.

To implement non-linear intensity transformations in a privacy--preserving system, it is necessary to evaluate logarithm and exponential functions using closed--form approximations, since the arguments of the functions are unknown. An applicable approximation for the logarithm, found in \cite{pcsc-paper}, is
% TODO: HOW ABOUT BGV
\begin{align}\label{eq:optimal_log_approximation}
	\begin{split}
		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
	\end{split}
\end{align}
where
\begin{align*}
	\begin{split}
	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
	&- 121239315x - 257804775\\
	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
	&+ 3122577).
	\end{split}
\end{align*}
This approximation can be computed under a homomorphic cryptosystem which supports floating--point operations by precomputing the value of $\log{16}$ in the plaintext domain.
% \begin{align}\label{eq:optimal_log_approximation}
% 	\begin{split}
% 		&\log\left(1+x\right) \\
% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
% 		&+ \log{16}.
% 	\end{split}
% \end{align}

% \subsubsection{Power-Law Transformation}
To apply the power-law transformation we can use partial sums of the infinite series,
\begin{align} \label{eq:power_approximation}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}},
\end{align}
which relies on the logarithm function.
For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.

### 2019-03-18 icmssp-paper/parts/02_03_facialrecognition.tex
Finished first pass of revisions

\subsubsection{Eigenfaces}
Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}. An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set. The number of resulting eigenfaces is equal to the number of face images in the training set.

@@

\subsection{Previous Implementations of Secure Facial Recognition}
Erkin, et al. \cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method. In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.

@@

Computing for the distances within Paillier would just be multiplying the encrypted sums together.
\begin{equation}
	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
\end{equation}

The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form. Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.

Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice. She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob. Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
\begin{equation}
	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
\end{equation}

The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
% This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.

The match-finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$. If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}. Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support. Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.

>>>>

% \subsubsection{Eigenfaces}
Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}. An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set. The number of resulting eigenfaces is equal to the number of face images in the training set.

@@

% \subsection{Previous Implementations of Secure Facial Recognition}
Erkin, et al. \cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method. In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.

@@

Computing for the distances within Paillier would just be multiplying the encrypted sums together.
\begin{equation}
	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
\end{equation}
The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form. Computing for $\left[\mathcal{S}_3\right]$ requires the use of the secure squaring protocol outlined in Table \ref{tab:flop_summary}.
% The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form. Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.

% Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice. She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob. Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
% \begin{equation}
% 	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
% \end{equation}

% The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
% This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.

The match-finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$. If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}. Getting the minimum among the encrypted distances involves comparing two numbers which can be performed using the DGK secure comparison protocol \cite{pieprzyk_efficient_2007}.

### 2019-03-18 icmssp-paper/parts/03_methodology.tex
Finished first pass of revisions

\subsection{Cryptosystem Implementation}
A wrapper library was created in Python that integrates the Paillier, DGK, and BGV cryptosystems into a unified interface.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
\end{itemize}

% [TO-DO: This is further explained in another paper.]
% We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
% The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
% This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.

% We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$. The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
% Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively. Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively. We define the secure real number operations as follows:
% \begin{description}
%   \item[Addition.]
%     To compute $E(c)=E(a+b)$ we compute
%     \begin{align*}
%       E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
%       E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
%     \end{align*}
%   \item[Scalar multiplication.]
%     To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
%     \begin{align*}
%       E(m_c) &= m_a \otimes E(m_b)\\
%       e_c &= e_a + e_b
%     \end{align*}
% \end{description}

\subsection{Non-Linear Intensity Transformations}
We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
% \subsubsection{Logarithm Transformation}
In order to perform the logarithm transformation under Paillier and DGK, we use the following closed-form approximation for $\log\left(1 + x\right)$ from~\cite{pcsc-paper}.
% TODO: HOW ABOUT BGV
\begin{align}\label{eq:optimal_log_approximation}
	\begin{split}
		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
	\end{split}
\end{align}
where
\begin{align*}
	\begin{split}
	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
	&- 121239315x - 257804775\\
	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
	&+ 3122577).
	\end{split}
\end{align*}
% \begin{align}\label{eq:optimal_log_approximation}
% 	\begin{split}
% 		&\log\left(1+x\right) \\
% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
% 		&+ \log{16}.
% 	\end{split}
% \end{align}

% \subsubsection{Power-Law Transformation}
To apply the power-law transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
We use partial sums of the following series, which relies on the logarithm function.
\begin{align}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align}
For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.

\subsection{Assessment of Homomorphic Encryption Schemes}
A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions. The processing time for all cases were recorded. All of the tests are done using Python 3.7.1 running on Linux.

\subsubsection{Image Quality of Intensity Transformations}
In this section, we discuss the image quality metrics we used for assessing the performance of non-linear intensity transformations.

We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex. However, only ten distinct facial images from the dataset were selected for the purposes of this test. Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.

For each cryptosystem, three image operations are tested:
\begin{enumerate}
	\item Image negation
	\item Logarithm transformation, with $c = 30$
	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
\end{enumerate}

@@

We perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011}. In describing each test, we let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
	\begin{align}
        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	The PSNR is ``an estimator for human visual perception of reconstruction quality.''~\cite{ahmed_benchmark_2016}. Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}, and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
	PSNR is defined by
	\begin{align}
        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2$ and $c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels. Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
\end{description}

>>>>

\subsection{System Implementation}
A wrapper library was created in Python that integrates the Paillier, DGK, and BGV cryptosystems into a unified interface.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
\end{itemize}

\subsection{Assessment of Homomorphic Encryption Schemes}
\subsubsection{Image Quality of Intensity Transformations}
We  obtained ten test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex. The images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
For each cryptosystem, three image operations are tested, as they are defined in Table \ref{tab:imageoperation_summary}:
\begin{enumerate}
	\item Image negation
	\item Logarithm transformation, with $c = 30$
	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
\end{enumerate}
The logarithm transformation was implemented using the approximation in Equation \ref{eq:optimal_log_approximation}, while the exponentiation in the power-law transformation was implemented by evaluating the sum of the first five terms of the infinite series in Equation \ref{eq:power_approximation}.

A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions. The processing time for all cases were recorded. All of the tests are done using Python 3.7.1 running on Linux.

@@

We perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011}. In describing each test, we let $R_i$ denote a value in an image $R$, where $1 \leq i \leq N$.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
	\begin{align}
        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	The PSNR is ``an estimator for human visual perception of reconstruction quality.''~\cite{ahmed_benchmark_2016}. Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}, and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
	PSNR is defined by
	\begin{align}
        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2$ and $c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels. Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
\end{description}
